---
title: "K-means"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Upload data
```{r}
inf <- read.csv("bank.csv", header = TRUE, encoding = "UNICOD")
inf <- subset(inf, select = -c(education,default,contact,pdays,poutcome,month,campaign,previous))
require(dplyr)
inf <- inf[, c("balance","duration")]
glimpse(inf)
```
#### Conclusion: For building a clustering model was used data on the availability of deposit account. Quantitative variables were left for modeling. Dataset does not require division into training and test samples and scaling.

# Elbow method to find optimal number of clusters
```{r}
library(stats)
wcss = vector()
for (i in 1:10) wcss[i] = sum(kmeans(inf, i)$withinss)
plot(1:10,
     wcss,
     type = "b",
     main = paste("The Elbow Method"),
     xlab = "Number of clusters",
     ylab = "WCSS")
```
#### Conclusion: Conclusion about the feasibility of identifying three clusters was made using the Elbow method.

# Fitting K-Means to the dataset
```{r}
set.seed(29)
model_km = kmeans(inf, 3)
#cluster cores
y_km = model_km$cluster
aggregate(inf,by=list(y_km),FUN=mean)
```
#### Conclusion: 3 clusters were described based on the k-means method.

# Visualising the clusters
```{r}
library(cluster)
clusplot(inf[,c('balance','duration')],
         y_km,
         lines = 0,
         shade = TRUE,
         color = TRUE,
         labels= 0,
         plotchar = FALSE,
         span = TRUE,
         main = paste('Clusters of customers'),
         xlab = 'balance',
         ylab = 'duration')
```
#### Conclusion: Was performed a visualization of clusters on a dataset.

# Comparing to HC
```{r}
#install.packages('clusteval')
library(clusteval)
model_hc <- hclust(dist(inf), method = "ward.D" )
y_hc <- cutree(model_hc, k = 3)
cluster_similarity(y_hc,y_km)
```
#### Conclusion: Obtained clusters intersect at 69.1%.