---
title: "Hierarchical Clustering"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Upload data
```{r}
inf <- read.csv("bank.csv", header = TRUE, encoding = "UNICOD")
inf <- subset(inf, select = -c(education,default,contact,pdays,poutcome,month,campaign,previous))
require(dplyr)
inf <- inf[, c("balance","duration")]
glimpse(inf)
```
#### Conclusion: For building a clustering model was used data on the availability of deposit account. Quantitative variables were left for modeling. Dataset does not require division into training and test samples and scaling.

# Hierarchical clustering
```{r}
model_hc <- hclust(dist(inf), method = "ward.D" )
plot(model_hc, main = paste('Dendrogram'))
```
#### Conclusion: Dendrogram was built using the Ward.D. method.

## Fitting HC to the dataset
```{r}
y_hc <- cutree(model_hc, k = 3)
#cluster cores
aggregate(inf,by=list(y_hc),FUN=mean)
#Cluster stat
inf$hc <- y_hc
table(inf$hc)
```
#### Conclusion: Based on a dendogram's analysis were detected 3 clusters.

## Plotting the dendrogram
```{r}
plot(model_hc, cex = 0.7, labels = FALSE)
rect.hclust(model_hc, k = 3, border = 2:5)
```
#### Conclusion: Was complited a visualization of clusters on the dendrogram.

### Visualising the clusters
```{r}
library(cluster)
clusplot(inf[,c("balance","duration")],
         y_hc,
         lines = 0,
         shade = TRUE,
         color = TRUE,
         labels= 0,
         plotchar = FALSE,
         span = TRUE,
         main = paste("Clusters"),
         xlab = "balance",
         ylab = "duration")
```
#### Conclusion: Was performed a visualization of clusters on the dataset.