---
title: "Data Preparation"
output: html_document
---

# Add packages
```{r warning: FALSE}
#install.packages("ggplot2")
#install.packages("dplyr")
#install.packages("psych")
#install.packages("caTools")
#install.packages("tidyr")
#Connect library
library (dplyr)
library(ggplot2)
library(tidyr)
```

# Upload data
```{r}
inf <- read.csv(file = "udemy.csv")
#Have a look at the data
#glimpse(inf)  
#head(inf)
info <- subset(inf, select = -c(id,title,url,avg_rating,avg_rating_recent,is_wishlisted,num_published_practice_tests,published_time,discount_price__currency,discount_price__price_string,price_detail__currency,price_detail__price_string,num_reviews,created))
info$is_paid <- as.logical(info$is_paid)
glimpse(info)
head(info)
```
#### Conclusion: num of observations - 13608, num of variables - 6

# Visualising

## Histogram
```{r}
library(ggplot2)
par(mfrow = c(1, 2))
hist(info$num_subscribers, col = 'dark blue', main = 'subscribers', xlab = 'Value')
hist(info$price_detail__amount, col = 'dark green', main = 'price', xlab = 'Value')
```
#### Conclusion: Variable price_detail__amount has a long tail

## Box-plot
```{r}
par(mfrow = c(1, 3))
boxplot(info$num_subscribers)
boxplot(info$price_detail__amount)
boxplot(info$num_published_lectures)
qplot(data = info, 
      x = is_paid, 
      y = num_subscribers, 
      geom = "boxplot")
```

#### Conclusion: Variables num_subscribers and num_published_lectures have some ejections. Paid resources have more atypical values of variable num_subscribers

## Violin
```{r}
qplot(data = info, 
      x = is_paid, 
      y = num_published_lectures, 
      geom = "violin")
```

#### Conclusion: Paid resources have more atypical values of variable num_published_lectures

# Statistics
```{r}
library(psych)
des <- describe(info)
View(des)
```
#### Conclusion: analysis of key indicators per each variable shows that variable discount_price__amount has 906 (=13111-12205) missing values. Variables num_subscribers,  num_published_lectures, discount_price__amount have ejections.

# Correlations
```{r}
info[is.na(info)] <- 0
pairs.panels(info, lm=TRUE, # linear fit
             method = "pearson", # correlation method
             hist.col = "#00AFBB")
```
#### Conclusion: Variable price_detail__amount is the most affected by the variable num_published_lectures

# Ejections (outside the three sigma)

## Remove the ejections (not recommended strategy)
```{r}
info_ej1 <- info[info$num_subscribers < mean(info$num_subscribers)+sd(info$num_subscribers)*3, ]
des1 <- describe(info_ej1$num_subscribers)
View(des1)
```
#### Conclusion: 13453 rows left after removing of ejections of variable num_subscribers 

## Replace with max
```{r}
info_ej2 <- info
info_ej2$num_subscribers <- ifelse(info$num_subscribers < mean(info$num_subscribers)+sd(info$num_subscribers)*3,info$num_subscribers,mean(info$num_subscribers)+sd(info$num_subscribers)*3)
des2 <- describe(info_ej2$num_subscribers)
View(des2)
#let's work with info_ej2
info <- info_ej2
```
#### Conclusion: replace with max is chosen to remove the ejections

# Missing data

## Delete N/A (not recommended strategy) 
```{r}
info_paid <- drop_na(info,price_detail__amount) #removing of NA price data of non paid resources for clean analytics. 13111 rows left
info_reduce <- drop_na(info_paid)
cat('there are',nrow(info_reduce),'rows in the info_reduce')
```
#### Conclusion: this way is bad for us, because we're losing a lot of data

## Fill n/a with neighboring values
```{r}
info_fill1 <- fill(info_paid, discount_price__amount, .direction = 'down')  
View(info_fill1)
cat('there are',nrow(info_fill1),'rows in the info_fill1')
```
#### Conclusion: filling NA with nbr values is obviously more effective

## Fill n/a with average or the most frequent
```{r}
info_fill2 <- info_paid
##with average for integer vars 
info_fill2$discount_price__amount <- ifelse(is.na(info_paid$discount_price__amount),round(mean(info_paid$discount_price__amount,na.rm = TRUE)),info_paid$discount_price__amount)
##the most frequent for categorical vars
info_fill3 <- info_paid
info_fill3$discount_price__amount <- ifelse(is.na(info_paid$discount_price__amount),which.max(table(info_paid$discount_price__amount)),info_paid$discount_price__amount)
View(info_fill2)
View(info_fill3)
#let's work with "filled with ave" data 
info <- info_fill2
```

# Splitting the dataset into the TRAIN set and TEST set
```{r}
set.seed(123)
library(caTools)
split = sample.split(info$num_subscribers, SplitRatio = 0.8)
info_train = subset(info, split == TRUE)
info_test = subset(info, split == FALSE)
#Write prepared data to the file
write.csv2(info_train, file = "udemy_train.csv")
write.csv2(info_test, file = "udemy_test.csv")
```
#### Conclusion: dataset is split into train set and test set. Related files are saved