---
title: "Support Vector Machine"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Upload data
```{r}
inf <- read.csv("bank.csv", header = TRUE, encoding = "UNICOD")
inf <- subset(inf, select = -c(education,default,contact,pdays,poutcome,month,campaign,previous))
require(dplyr)
inf <- inf %>%
      mutate(deposit = ifelse(deposit == "no",0,1))
glimpse(inf)
```
# Features Scaling
```{r}
inf <- inf[,c("balance","duration","deposit")]
sc <- scale(inf)
inf$balance <- sc[,c("balance")]
inf$duration <- sc[,c("duration")]
glimpse (inf)
```
#### Conclusion: For modeling were chosen quantitative variables, because they turned out to be significant. We scaled the quantitative variables.

# Splitting the dataset into the TRAIN set and TEST set
```{r}
set.seed(123)
library(caTools)
split = sample.split(inf$deposit, SplitRatio = 2/3)
inf_train = subset(inf, split == TRUE)
inf_test = subset(inf, split == FALSE)
```
#### Conclusion: dataset is split into train set and test set.

# Fitting linear model
```{r}
#install.packages("e1071")
library(e1071)
class_svm_l = svm(deposit ~ ., data = inf_train, kernel = "linear")
summary(class_svm_l)
```
#### Conclusion: Linear kernel is chosen to teach the basic model based on the reference vectors method.

# Predicting
```{r}
p <- predict(class_svm_l, inf_test[, c("balance","duration")])
y <- ifelse(p > 0.5, 1, 0)
```
#### Conclusion: Object classes (vector y) are defined.

# Confusion Matrix
```{r}
cm = table(inf_test[,"deposit"],y)
print(cm)
```
#### Conclusion: Accuracy of the model - (1789+711)/3721=67.2%. Part of incorrectly classified cases - (1052+169)/3721 = 32.8%. Sensitivity of the model is 711/(711+1052)=40.3%, specificity is 1789/(1789+169)=91.4%, ie the model is more sensitive to the detection of negative cases.

# Visualising the Test set results
```{r}
xgrid = expand.grid(balance = inf_test$balance, duration = inf_test$duration)
ygrid = predict(class_svm_l, xgrid)
plot(xgrid, col = as.numeric(ygrid), pch = 20, cex = 1)
points(inf_test[, c('balance','duration')], col = green, pch = 20)
```
#### Conclusion: R can't load the graph.

# Fitting RBF-kernel model
```{r}
library(e1071)
class_svm_r = svm(deposit ~ balance + duration, data = inf_train, kernel = 'radial')
summary(class_svm_r)
```
#### Conclusion: Nonlinear kernel was chosen to teach the model based on the reference vectors method.

# Predicting
```{r}
p <- predict(class_svm_r, inf_test[, c('balance','duration')])
y <- ifelse(p > 0.5, 1, 0)
```
#### Conclusion: Object classes (vector y) are defined.

## Confusion Matrix
```{r}
cm = table(inf_test[, 'deposit'], y)
print(cm)
```
#### Conclusion: Accuracy of the model - (1532+1177)/3721=72.8%. Part of incorrectly classified cases - (586+426)/3721 = 27.2%. Sensitivity of the model is 1177/(1177+586)=66.8%, specificity is 1532/(1532+426)=78.2%, ie the model is more sensitive to the detection of positive cases.

# Visualising the Test set results
```{r}
library(ggplot2)
set = inf_test[,c('balance','duration','deposit')]
X1 = seq(min(set['balance']) - 1, max(set['balance']) + 1, by = 0.1)
X2 = seq(min(set['duration']) - 1, max(set['duration']) + 1, by = 0.1)
grid_set = expand.grid(X1, X2)
colnames(grid_set) = c('balance', 'duration')
p_grid = predict(class_svm_r, grid_set)
y_grid <- ifelse(p_grid > 0.5, 1, 0)
plot(set[, -3],
     main = 'SVM',
     xlab = 'balance', ylab = 'duration',
     xlim = range(X1), ylim = range(X2))
contour(X1, X2, matrix(as.numeric(y_grid), length(X1), length(X2)), add = TRUE)
points(grid_set, pch = '.', col = ifelse(y_grid == 1, 'tomato', 'springgreen3'))
points(set, pch = 21, bg = ifelse(set[, 3] == 1, 'red3', 'green4'))
```
#### Conclusion: Ñustomers who do not have deposits are marked in green on a graph, and those who do are in red. Zone of high probability of taking a deposit is marked in red.